A systematic search for transiting planets using \KT

### 2015-02-12 ms.tex
editing model section

The key insight in our transit search method that sets it apart from the
other standard procedures is that no de-trending is necessary.
Instead, we can fit for the noise (or trends) and signal simultaneously.
This is theoretically appealing because it will be more sensitive to low
signal-to-noise transits.
The main reason for this is that the signal is not exactly orthogonal to the
systematics and the de-trending will over-fit causing the signal to be
distorted and weaker.
In order to reduce this effect, most procedures use a very rigid model for
the trends.
For \KT, this has been implemented by asserting that the centroids contain
all of the information needed to describe the trends \citep{Vanderburg:2014,
Aigrain:2015, Crossfield:2015}.
In the \kepler\ pipeline, this is implemented by only allowing a small number
of PCA components to contribute to the fit in the \pdc\ procedure.

Physically, the motivation for our model---and the \pdc\ model---is that every
star on the detector should be affected by same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Crossfield:2015} but
out more flexible model should capture the systematic effects more robustly
but there is a risk of over-fitting.
\Fig{corr} shows the application of this model to a light curve with no known
transit signals.

To avoid over-fitting in our pipeline, we simultaneously fit for the transit
signal and the trends using a rigid model for the signal and a relatively
flexible model for the noise.
Specifically, we model the light curve as being generated by linear
combination of the 150 basis light curves and a ``box'' transit model at a
given period and phase.

@@

\bibliography{k2}

@@

\clearpage

>>>>

The key insight in our transit search method that sets it apart from the
other standard procedures is that no de-trending is necessary.
Instead, we can fit for the noise (or trends) and signal simultaneously.
This is theoretically appealing because it will be more sensitive to low
signal-to-noise transits.
The main reason for this is that the signal is not exactly orthogonal to the
systematics and any de-trending will over-fit; decreasing the amplitude of the
signal and distorting its shape.
In order to reduce this effect, most procedures use a very rigid model for
the trends.
For \KT, this has been implemented by asserting that the centroids contain
all of the information needed to describe the trends \citep{Vanderburg:2014,
Aigrain:2015, Crossfield:2015}.
In the \kepler\ pipeline, this is implemented by only allowing a small number
of PCA components to contribute to the fit in the \pdc\ procedure.
Instead, we will use a large number of ELCs---a very flexible model---and
use a physically motivated method to avoid over-fitting.

Physically, the motivation for our model---and the \pdc\ model---is that every
star on the detector should be affected by the same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs as a result of the
varying flat field.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Aigrain:2015,
Crossfield:2015} but our more flexible model should capture the systematic
effects more robustly.
For example, \Fig{corr} shows the application of our model---with 150
ELCs---to a light curve with no known transit signals and the precision is
excellent.
If, however, we were to apply this model blindly to a light curve with
transits, we would be at risk of over-fitting and decreasing the amplitude of
the signal.

To avoid over-fitting, in our pipeline we simultaneously fit for the transit
signal and the trends using a rigid model for the signal and a relatively
flexible model for the noise.
Specifically, we model the light curve as being generated by linear
combination of 150 ELCs and a ``box'' transit model at a specific period,
phase, and duration.
The mathematical details are given in \app{math} but in summary, since the
model is linear, we can analytically compute the likelihood
function---conditioned on a specific period, phase, and duration---for the
depth \emph{marginalized over the systematics model}.
This computation is expensive but, as described in the following sections, it
is possible to scale the method to a \KT-scale dataset.

It is worth noting that this model can be equivalently thought of as a
(computationally expensive) generalization of the ``Box Least Squares''
\citep[\project{BLS};][]{bls} method to a more sophisticated description of
the noise and systematics.
Therefore, any existing search pipeline based on \project{BLS} could, in
theory, use this model as a drop-in replacement, although some modifications
might be required for computational tractability.

@@

@@

\clearpage
\bibliography{k2}
\clearpage
